### 2025-12-12 README.Rmd
swap hex logo
🤫

# infer R Package <img src="man/figures/logo.png" alt="A hexagonal logo. A silhouette of a fir tree sits atop green text, reading 'infer'. The logo has a white background and green border." align="right" width=280 />

>>>>

# infer R Package <img src="man/figures/logo.png" alt="A hexagonal logo. A green silhouette of a fir tree sits atop black text, reading 'infer'. The logo has a background in two shades of blue, resembling the Oregon license plate." align="right" width=280 />
